ACNP 2024 MS ANXIETY

### 2024-08-13 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
promis_analyses

>>>>

####Test promis*anxiety dose  stats
#####Physical and Mental Health together
```{r phsy_and_mental_step_x_anxiety_dose}
###
df_for_promis_plot_mental_vs_physical_healthy_test <- df_people_with_promis_data_scores_added_unique %>%
  group_by(EMPI) %>%
  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
  mutate(phys_mental_diff_score = physical_health_score-mental_health_score) %>%
  dplyr::select(EMPI,
                anxiety_dose,
                physical_health_score,
                mental_health_score,
                phys_mental_diff_score)

#anxiety_dose  -0.7345     0.2946  -2.493   0.0153 *  
anxiety_dose_x_phys_score <- lm(physical_health_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
summary(anxiety_dose_x_phys_score)

#anxiety_dose  -1.1181     0.2681  -4.171 9.59e-05 ***
anxiety_dose_x_mental_score <- lm(mental_health_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
summary(anxiety_dose_x_mental_score)

#anxiety_dose   0.3836     0.2391   1.605    0.114
anxiety_dose_x_diff_score <- lm(phys_mental_diff_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
summary(anxiety_dose_x_diff_score)
```

##### Physical and Mental Health x anxiety dose intx
```{r phys_and_mental_x_anxiety_dose}
###
df_for_promis_plot_mental_vs_physical_healthy_no_summarize <- df_people_with_promis_data_scores_added_unique %>%
  group_by(EMPI) %>%
  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
  mutate(anxiety_dose = as.numeric(anxiety_dose)) %>%
  dplyr::select(EMPI,
                anxiety_dose,
                physical_health_score,
                mental_health_score) %>%
  gather(health_variable, PROMIS_Score, -anxiety_dose, -EMPI)

#anxiety_dose                                       -1.1181     0.2816 88.0000  -3.970 0.000146 ***, others NS
anxiety_dose_by_health_var_score <- lmer(PROMIS_Score ~anxiety_dose*health_variable + (1|EMPI), df_for_promis_plot_mental_vs_physical_healthy_no_summarize)
summary(anxiety_dose_by_health_var_score)
